When does vapor pressure deficit drive or reduce evapotranspiration?

### 2018-02-15 doc/paper/vpd_et_paper.tex
a few more commengts to do

The Medlyn model for stomatal conductance has been shown to behave very well across PFTs, compared to other models from the leaf to ecosystem scale \citep[, CITE ZHOU ET AL AS WELL** ??][]{Lin_2015, Zhou_2015}. It is adapted at the ecosystem scale by multiplying $g_{l-s}$ by leaf area index (LAI) and converting units to m s$^{-1}$:

>>>>

The Medlyn model for stomatal conductance has been shown to behave very well across PFTs, compared to other models from the leaf to ecosystem scale \citep[ZHOU ET AL AS WELL** ?? - Pierre says Zhou 2014][]{Lin_2015, Zhou_2015}. It is adapted at the ecosystem scale by multiplying $g_{l-s}$ by leaf area index (LAI) and converting units to m s$^{-1}$:
